---
title: 'Verb'
author: Raju Rimal
date: '2017-09-25'
slug: verb
categories:
  - Referense
tags: [referense, verb]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  comments = NULL,
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
options(knitr.kable.NA = '')
```

```{r, eval = FALSE}
library(tidyverse)
verb_list <- readxl::read_xlsx("../../static/verb-list.xlsx")
irregular <- verb_list %>% 
    filter(Gruppe %in% c("UV", "UV/HV")) %>% 
    select(-Gruppe)
# knitr::kable(irregular, format = "html",
#     col.names = paste0("**", names(irregular), "**"))
DT::datatable(irregular)
```

| **English**   | **Infinitiv** | **Presens** | **Preteritum** | **Perfektum** |
|---------------+---------------+-------------+----------------+---------------|
| to be         | å være        | er          | var            | har vært      |
| to eat        | å spise       | spiser      | spiste         | har spist     |
| to teach      | å lese        | leser       | leste          | har lest      |
| to write      | å skriv       | skriver     | skrev          | har skrevet   |
| to go         | å dra         | drar        | dro            | har dratt     |
| to walk       | å gå          | går         | gikk           | har gått      |
| to stand      | å stå         | står        | stod           | har stått     |
| to understand | å forstå      | forstår     | forstod        | har forstått  |
| to say        | å si          | sier        | sa             | har sagt      |
| to see        | å se          | ser         | så             | har sett      |
